% !TEX program = xelatex
\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

% \usepackage{enumitem}
\usepackage{graphicx}



\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Jieke(Jack) Wu}

\basicInfo{
  % (412) 996-7548 $\bullet$
  \href{mailto:jack666@mail.ustc.edu.cn}{jack666@mail.ustc.edu.cn} $\bullet$
  \href{https://github.com/a-green-hand-jack}{GitHub} $\bullet$
  \href{https://a-green-hand-jack.github.io/}{Homepage}
}

\section{Education}

\datedsubsection{\textbf{\href{https://www.ustc.edu.cn/}{University of Science and Technology of China}}, Hefei, China}{08/2021 -- 06/2025 (expected)}
School of Life Sciences, major in Biological Technology 
\begin{itemize}
  \item GPA:3.40/4.30,Rank:27/90
  \item Core Courses: \\Linear Algebra B1(90/100);Electromagnetism B;(90/100); Undergraduate 
  Research Project(A+);\\Undergraduate Innovation and Entrepreneurship Training Program(A+)
\end{itemize}

% \datedsubsection{\textbf{\href{http://www.xgdfz.com/}{The Middle School Attached To Northwestern Polytechnical University}}, Xi'an, China}{08/2018 -- 06/2021}

\section{Experience}

  \datedsubsection{\textbf{Hierarchical transformer for genomics}}{Research Assistant}
  \datedsubsection{\href{https://zhanglab-aim.github.io/members/fzzhang}{Cedars-Sinai Medical Center, Dr.Zijun Zhang}\\\href{https://chenwydj.github.io/}{UC Berkeley, Dr.Wuyang Chen}}{03/2024 -- 08/2024}
    \begin{itemize}
      \item Investigated Concealed Information within DNA Sequences using Deep Learning.
      \item Explored how to enhance the model’s perception of DNA information by integrating the global and local information of DNA sequences.
    \end{itemize}

  \datedsubsection{\textbf{Training-free Design of Data-centric Augmentations with Principles}}{Research Assistant}
  \datedsubsection{\href{https://chenwydj.github.io/}{UC Berkeley, Dr.Wuyang Chen}}{06/2023 -- 02/2024}
    \begin{itemize}
      \item Discovered principled metrics that effectively gauge both data quality and its interaction with DNN without the need for extensive DNN training,enabling training-free augmentation design with minimal computation costs.
      \item \href{https://openreview.net/forum?id=kmAdBRaShI}{This project} was published at ICML 2024 Workshop AI4Science
    \end{itemize}
    
  \datedsubsection{\textbf{Isolation of bacteriophages targeting gut bacteria}}{Research Assistant}
  \datedsubsection{\href{http://biomed.ustc.edu.cn/2022/0505/c24993a553532/page.htm}{University of Science and Technology of China, Prof.Yi Duan}}{01/2023-- 05/2024}
  \begin{itemize}
    \item This study established an improved in vitro culture system for \textit{Akkermansia muciniphila} (Akk), simplifying and enhancing the user-friendliness compared to previous systems, while also eliminating \textit{Cutibacterium acnes} contamination.
    \item Successfully isolated and purified Akk-targeting phages from wastewater, facilitating the development of a phage library for gut microbiome research.
    \item This project was rated as an excellent school-level project that year.
  \end{itemize}

  \datedsubsection{\textbf{\small{Biodegradable needles for transdermal delivery in biofilm-infected chronic wounds}}}{Research Assistant}
  \datedsubsection{\href{https://sz.ustc.edu.cn/rcdw_show/44.html}{Suzhou Institute for Advanced Research,Prof.Xiaorong Xu}}{11/2022 -- 09/2023}

    \begin{itemize}
      \item Proficiency in finite element simulation software (COMSOL and Abaqus) for conducting simulation tasks.
      \item Designed a long microneedle for the treatment of deep-seated tissue infections.
      \item Introduced a novel injection molding method for the cost-effective and convenient production of long or microneedles with complex geometrical structures.
      \item This project was rated as an excellent school-level project that year.
      \item Based on this work, we plan to publish a patent, which is currently under review.
    \end{itemize}

  \datedsubsection{\textbf{\small{Isolation and identification of cyanobacteria and cyanophages from Lake Chaohu}}}{Research Assistant}
  \datedsubsection{\href{https://czlab.ustc.edu.cn/}{Laboratory of Biochemistry \& Structural Biology, Prof.Congzhao Zhou}}{09/2022 -- 06/2023}
    \begin{itemize}
      \item Successfully isolated three strains of cyanobacteria from Lake Chaohu water samples.
      \item Isolated some cyanophages from Lake Chaohu water samples using these isolated cyanobacteria strains.
      \item Thanks to this work, we received an award at the National University Life Science Competition in the same year.
    \end{itemize}

\section{Selected Awards}
  \begin{itemize}
      \item Outstanding School-Level Project: Undergraduate Innovation and Entrepreneurship Training Program \hfill 2024
      \item Outstanding School-Level Project: College Student Research Program \hfill 2023
      \item A Prize in the 8th National University Life Science Competition \hfill 2023
      \item Outstanding Undergraduate Scholarship  \hfill 2024, 2023, 2022, 2021
  \end{itemize}

\section{Publications}

\begin{itemize}
  \item \textbf{Jieke Wu}, Wei Huang, Mingyuan Bai, Xiaoling Hu, Yi Duan, Wuyang Chen. "Training-free Design of Augmentations with Data-centric Principles." \emph{ICML 2024 Workshop AI4Science}.
\end{itemize}

\section{Skills}
  \textbf{Programming Languages:} \small Python, C/C++, Matlab (ranked by proficiency)

  \textbf{Tools and Frameworks:} \small HuggingFace, PyTorch, Git, \LaTeX (sorted by usage frequency) 


\end{document}
